The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
fix cite laforge
reflow intro
edit double coarse

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure 1,
@Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO: something broken here?? -->
Further, for social interactions or associations to occur individuals must share
space, and thus have overlapping home ranges. In the context of the social
environment, home range overlap is a relatively coarse scale of sociality across
which individuals share space over larger spatial and temporal scales [e.g.
@Piza_Roca_2018]. <!-- what is going on here -->Although the social environment clearly scales spatially and
temporally, it remains unclear whether coarser scales of sociality, including
social association and home range overlap, vary predictably with social
interaction [@Castles_2014; @Farine_2015a]. Thus, we define social scale as the
type of social relationship observed that can be explicitly defined and measured
[@Farine_2015a]. <!-- Farine references comes out as D.R. Farine 2015 -->

>>>>

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure 1,
@Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO: something broken here?? -->
Further, for social interactions or associations to occur individuals must share
space, and thus have overlapping home ranges [@VanderWal_2014]. In the context
of the social environment, home range overlap is an example of how animals share
space over coarser spatial and temporal scales (e.g. Piza-Roca et al. 2018).
Although the social environment clearly scales spatially and temporally, it
remains unclear whether coarser scales of sociality, including social
association and home range overlap, vary predictably with social interaction
[@Castles_2014;
@Farine_2015a]. Thus, we define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a]. <!--
Farine references comes out as D.R. Farine 2015 -->
